\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{titlesec}

\title{\textbf{CERN Open Hardware Licence Version 2 -- Strongly Reciprocal (CERN-OHL-S v2)}}
\date{}

\begin{document}
\maketitle
\onehalfspacing

\section*{Preamble}

CERN has developed this licence to promote collaboration among hardware designers 
and to provide a legal tool which supports the freedom to use, study, modify, 
share and distribute hardware designs and products based on those designs.

This licence applies to hardware documentation and design materials.

\section*{1. Definitions}

\textbf{Documentation} means design materials including, but not limited to, 
schematics, layout files, bill of materials, simulation models, and associated files.

\textbf{Source} means the preferred form of the Documentation for making modifications.

\textbf{Product} means any device or physical object made using the Documentation.

\textbf{Licensee} means any person or entity exercising rights under this Licence.

\section*{2. Applicable Licence}

This Licence is CERN-OHL-S v2.

\section*{3. Grant of Rights}

You are granted a worldwide, royalty-free, non-exclusive licence to:

\begin{itemize}
\item Use the Documentation;
\item Modify the Documentation;
\item Manufacture, have manufactured, distribute and use Products;
\item Distribute Documentation and Products.
\end{itemize}

\section*{4. Strong Reciprocity}

If you distribute modified Documentation or Products, you must:

\begin{itemize}
\item Make the complete corresponding Source available;
\item License it under CERN-OHL-S v2;
\item Provide access to modifications in the same format.
\end{itemize}

\section*{5. Patent Licence and Retaliation}

Each Contributor grants a patent licence covering necessary patent claims.

If you initiate patent litigation alleging infringement by the Documentation 
or a Product, your licence under this agreement terminates.

\section*{6. Disclaimer}

The Documentation is provided \textbf{``as is''}, without warranty of any kind.

\section*{7. Limitation of Liability}

In no event shall contributors be liable for damages arising from use of the Documentation.

\section*{Full Official Text}

The complete and authoritative version of the CERN-OHL-S v2 licence is available at:

\url{https://ohwr.org/project/cernohl/wikis/Documents/CERN-OHL-version-2}

This LaTeX rendering is provided for documentation packaging only.
For legal purposes, refer to the official text.

\end{document}
